```{r code = readLines("R/opts_chunk.R"), include=FALSE}
```

## pkr Shiny 

- `pkr Shiny` <https://asan.shinyapps.io/pkrshiny>
- `pkr Shiny` is open to everyone. We are happy to take your input. Please fork the repo, modify the codes and submit a pull request. <https://github.com/asancpt/pkrshiny>
- We are actively developing R pacakges, Shiny Apps, and Edison Science Apps regarding clinical pharmacology and pharmacometrics. Please check here. <https://asancpt.github.io/softwares>

### Installation of pkr R Package

```r
install.packages("pkr")
library(pkr)
NCA(Theoph, "Subject", "Time", "conc", dose=320, uConc="mg/L")
```

### Help

- `pkr` package help <https://cran.r-project.org/web/packages/pkr/pkr.pdf>

### Dataset

- `Theoph`: Oral 320 mg (N=12) <http://stat.ethz.ch/R-manual/R-devel/library/datasets/html/Theoph.html>
- `Indometh`: IV 25 mg (N=6) <http://stat.ethz.ch/R-manual/R-devel/library/datasets/html/Indometh.html>
- `sd_oral_richpk`: Oral 5000mg (N=50) <https://github.com/dpastoor/PKPDdatasets>
- `sd_iv_rich_pkpd`: IV diverse dosing (N=60) <https://github.com/dpastoor/PKPDdatasets>

### CDISC materials

- [CDISC SDTM Implementation Guide 3.2 PDF ](https://www.cdisc.org/sites/default/files/members/standard/foundational/sdtmig/sdtmig_20v3.2_20noportfolio.pdf)
- [CDISC Terminology PDF](https://evs.nci.nih.gov/ftp1/CDISC/SDTM/SDTM%20Terminology.pdf)

### References

Gabrielsson J, Weiner D. Pharmacokinetic and Pharmacodynamic Data Analysis - Concepts and Applications. 5th ed. 2016.

Shargel L, Yu A. Applied Biopharmaceutics and Pharmacokinetics. 7th ed. 2015.

Rowland M, Tozer TN. Clinical Pharmacokinetics and Pharmacodynamics - Concepts and Applications. 4th ed. 2011.

Gibaldi M, Perrier D. Pharmacokinetics. 2nd ed. revised and expanded. 1982.

### Bibliography of R packages

```{r}
Cit <- sapply(MyLib, function(x) print(citation(x), style = "html"))
```
